Continuous Reinforcement Learning

### 2018-06-12 magnitudes.tex
[ADD] Intuitions introduction.

>>>>

However, some reinforcement learning algorithms such as \emph{Q-Learning} are
ill-behaved in the regime of small time discretization. In what follow, we
analyze in an handwavy manner the reason for this failure, and give an alternative
algorithm that remains viable in the limit of small discretizations.
